---
title: "India COVID-19"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    vertical_layout: fill
    logo: images/cc_2.png
    favicon: images/favicon.png
    
editor_options: 
  chunk_output_type: console
---
<style>                     
.navbar {
  background-color:#033240;
  border-color:black;
}
</style>

<script>
$('.navbar-logo').wrap('<a href="https://cognitivecare.com/" target=_blank>', );
</script>

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(highcharter)
library(plotly)

confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"

ind <- read.csv("./data/complete.csv")
ind <- ind %>%
        mutate(date = as.Date(Date, format = "%d-%m-%Y"))%>%
        mutate(confirmed = Total.Confirmed.cases..Indian.National. + Total.Confirmed.cases...Foreign.National..) %>% 
        pivot_longer(cols = c(confirmed, Cured, Death ), names_to = "type", values_to = "cases")%>% 
        mutate(type = recode(type, Cured = "recovered", Death = "death"))%>%
        filter(cases !=0)%>% 
        select(-c(Total.Confirmed.cases..Indian.National., Total.Confirmed.cases...Foreign.National.., Date)) %>%
        rename(region = Name.of.State...UT)
colnames(ind) <- tolower(colnames(ind))

## create three dataframes
df <- ind %>%
        group_by(region, type) %>%
        filter(date == max(date)) %>%
        pivot_wider(names_from = type,values_from = cases)%>%
        arrange(-confirmed)%>%
        mutate(unrecovered = confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)) %>%
        ungroup()%>%
        mutate(region = trimws(region))%>%
        mutate(region = factor(region, levels = region))%>%
        select(-c(latitude, longitude, date))


df_daily <- ind %>%
        group_by(date, type)%>%
        summarise(total = sum(cases, na.rm =T))%>%
        pivot_wider(names_from = type, values_from = total)%>%
        mutate(active = confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death))%>%
        ungroup()


df1 <- ind %>% filter(date == max(date))
df_confirmed <- df1 %>% 
              filter(type == "confirmed")%>%
              select(name=region, lat=latitude, lon=longitude, z=cases)
df_death <- df1 %>% 
              filter(type == "death")%>%
              select(name=region, lat=latitude, lon=longitude, z=cases)
df_rec <- df1 %>% 
              filter(type == "recovered")%>%
              select(name=region, lat=latitude, lon=longitude, z=cases)
df_bar <- df %>% select(region, active=unrecovered, recovered, death) %>% 
              pivot_longer(c(active, recovered, death), names_to = "type", values_to = "cases")%>%
              mutate(type = factor(type, levels = c("active", "recovered", "death")))

```

Overview
=======================================================================
row
-----------------------------------------------------------------------

### confirmed {.value-box}

```{r}

valueBox(value = paste(format(sum(df$confirmed), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed Cases", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```


### active {.value-box}

```{r}
valueBox(value = paste(format(sum(df$unrecovered, na.rm = TRUE), big.mark = ","), "", sep = ""), 
         caption = "Active Cases", icon = "fas fa-ambulance", 
         color = active_color)
```

### recovered {.value-box}

```{r}
valueBox(value = paste(format(sum(df$recovered, na.rm = TRUE), big.mark = ","), "", sep = ""), 
         caption = "Recovered Cases", icon = "fas fa-heartbeat", 
         color = recovered_color)
```

### death {.value-box}

```{r}

valueBox(value = paste(paste(format(sum(df$death, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(df$death, na.rm = TRUE) / sum(df$confirmed), 1), 
                       "%)", sep = "")),
         caption = "Death Cases", 
         icon = "fas fa-bed", 
         color = death_color)
```

Row {data-height=850}
-----------------------------------------------------------------------

### **Total number of COVID-19 cases across India**

```{r}
hcmap("countries/in/custom/in-all-disputed", showInLegend = FALSE, nullColor = "#d6d6d6") %>% 
        hc_add_series(data = df_confirmed, type = "mapbubble",
                      name = "Confirmed", maxSize = '10%', color = confirmed_color)%>%
        hc_add_series(data = df_death, type = "mapbubble",
                      name = "Death", maxSize = '10%', color = "red")%>%
        hc_add_series(data = df_rec, type = "mapbubble",
                      name = "Recovered", maxSize = '10%', color = "blue")%>%
        hc_mapNavigation(enabled = TRUE) 

```

### **Total COVID-19 cases: States and UTs**

```{r}
ggplotly(ggplot(df_bar, aes(x=region, y=cases, fill = type))+ 
           geom_col(position = position_stack(reverse = TRUE)) +  coord_flip() +
           scale_fill_manual(values = c("active" = confirmed_color, "recovered" = "forestgreen", "death"="red")) +
           scale_x_discrete(limits = rev(levels(df_bar$region))) +
           theme_minimal()+
           theme(axis.title.y = element_blank(), legend.title = element_blank()) 
)
```

Row {data-height=150}
-----------------------------------------------------------------------

### updates #EDIT THIS MANUALLY {.no-title}

**Click on the legends to show/hide particular information**

**Updated on 20.03.2020 at 09:00 AM** 


### Sources {.no-title}
**Sources**

1. [Ministry of Health and Family Welfare](https://www.mohfw.gov.in/) 
2. [Indian Council of Medical Research](https://www.icmr.nic.in/) 


### Chart C:MANUALLY{.value-box}

```{r}

valueBox(value = prettyNum(14175, big.mark = ","),
         caption = "Total number of samples tested for SARS-CoV2 (19th March,6 PM)", 
         icon = "fas fa-vial")
```

### PASSENGERS MANUALLY {.value-box}

```{r}

valueBox(value = prettyNum(1431734, big.mark = ","), 
         caption = "Total number of passengers screened at airport", 
         icon = "fas fa-plane-arrival", 
         color = "#ff6699")
```
